Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-11 main.tex
conclusions slightly edited

 \heftbl and \heftblc can schedule all workflows in a normal cluster and approximately a half of them in a memory-constrained
    one.
    They provide a runtime that scales well with the growing size of a workflow.

    \heftmm can schedule even the largest workflows even on the memory-constrained cluster.
    It is the only heuristic that had $100\%$ success rate.
    However, the makespans it produces are larger than those of the the other two

Extend to heterogeneous bandwidths.

Further variability commented out from the paper: changing DAG structure; changing platform...

>>>>

 \heftbl and \heftblc can schedule all workflows in a normal cluster and approximately half of them in a memory-constrained
    one.
    They provide a running time that scales well with the growing size of a workflow.

    \heftmm can schedule even the largest workflows even on the memory-constrained cluster.
    It is the only heuristic that has $100\%$ success rate in our experiments.
    However, the makespans it produces are larger than those of the the other two.

\begin{itemize}
  \item Extend to heterogeneous bandwidths. 
  \item Further variability commented out from the paper: changing DAG structure; changing platform...
\end{itemize}
